Einstein's gravity from a polynomial affine model

### 2015-10-27 AffGR-PRD.tex
More Appendix: Dim. Anal.

In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant. A straightforward dimensional counting shows the impossibility of other contributions in to the action, \hl{see Appendix ...}. Interestingly, the above action turns to be power-counting renormalizable, which does not guarantees renormalizability but is a good signal. The structure of the model yields no three-point graviton vertices, which might allow to overcome  the no-go theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}. It is worth mentioning that all coupling constants are dimensionless, which might be a hint of conformal invariance of the model~\cite{Buchholz:1976hz}.

@@

Until now, the most general diffeomorphism-invariant and power-counting renormalizable (gravitational) theory for an affine connection has been built, and we have showed that in a certain sector it is equivalent to General Relativity. In what follows, we show an attempt of including scalar matter into the model. The theory does not require a spacetime metric, but instead we should consider the most general $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields, and use it to build Lagrangian densities for the matter content. Following our precept, the matter content ---scalar matter--- should couple to $\mathfrak{g}^{\mu\nu}$, given by %% which for Eq.~\eqref{4dfull} is
\begin{dmath}
  \mathfrak{g}^{\mu\nu} = \alpha \, \nabla_\lambda T^{\mu,\nu\lambda} + \beta \, A_\lambda T^{\mu,\nu\lambda} + \gamma \, \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma},
\end{dmath}
with $\alpha$, $\beta$ and $\gamma$ arbitrary coefficients.

>>>>

In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant. A straightforward dimensional counting shows the impossibility of other contributions in to the action, see Appendix~\ref{DA}. Interestingly, the above action turns to be power-counting renormalizable, which does not guarantees renormalizability but is a good signal. The structure of the model yields no three-point graviton vertices, which might allow to overcome  the no-go theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}. It is worth mentioning that all coupling constants are dimensionless, which might be a hint of conformal invariance of the model~\cite{Buchholz:1976hz}.

@@

Until now, the most general diffeomorphism-invariant and power-counting renormalizable (gravitational) theory for an affine connection has been built, and we have showed that in a certain sector it is equivalent to General Relativity. In what follows, we show an attempt of including scalar matter into the model. The theory does not require a spacetime metric, but instead we should consider the most general $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields, and use it to build Lagrangian densities for the matter content. Following our precept, the matter content ---scalar matter--- should couple to $\mathfrak{g}^{\mu\nu}$, given by
\begin{dmath}
  \mathfrak{g}^{\mu\nu} = \alpha \, \nabla_\lambda T^{\mu,\nu\lambda} + \beta \, A_\lambda T^{\mu,\nu\lambda} + \gamma \, \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma},
  \label{geng}
\end{dmath}
with $\alpha$, $\beta$ and $\gamma$ arbitrary coefficients.
